Transforming Trash as an Artistic Act

### 2015-12-29 chapter3_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7

Using non-art object can be considered as moving away from the purification of art \todo{ref req}. It is a composition of different fragments and pieces. Rather than the traditional way of painting on canvas modern artists composed their work with the combination of various objects from different context. With this approach works can be examined in multi-dimensional context.

@@

One of the earliest and notable examples of collage is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope that was used to frame the picture. Picasso combined painting with already existing materials. As mentioned in the name of the work, Picasso give clues of the parts of it. For instance the oval canvas and the rope around it represent the table. Pasted chair caning signifies the chair within the table. On the table folded paper shadow represent newspaper. Further there is a cut out lemon painted onto the table. \paraphrase{The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness. This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.}

@@

\paraphrase{Artifact exploration promotes historical thinking, literacy investigation, and cultural expression (Higgs \& McNeal, 2006; Levstik \& Barton, 2001; Morris, 1998). Meanings are embedded within cultural artifacts and language (Vygotsky, 1978).}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
  \caption{Dick Jewell}
  \label{fig:DickJewell_FoundPhotos}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
  \caption{Road Kill by Filomena Cruz}
  \label{fig:FilomenaCruz_RoadKill_ReVista}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Vic Muniz, Pictures of Garbage}
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

@@

They build their musical instruments from what is available around. This project can be seen as a bricolage practice. Dictionary meaning; something constructed using whatever was available at the time. \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.

\paraphrase{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}

@@

In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical potraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects. The people in the figure X is General Jefferson C. Davis who was an officer at United States Army in 19th-century. Selected persons can be viewed as a member of the higher or ruling class of society. Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good. Or vice versa. She probably use trash to provocate social elite of that time.

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
  \caption{Kim Alsbrooks, The White Trash Series}
  \label{fig:Alsbrooks}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=7cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, Art Bin}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

@@

Examples are not limited with these. Even if \paraphrase{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

>>>>

Using non-art object can be considered as moving away from the purification of art. It is a composition of different fragments and pieces. Rather than the traditional way of painting on canvas modern artists composed their work with the combination of various objects from different context. With this approach works can be examined in multi-dimensional context.

@@

One of the earliest and notable examples of collage is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth which is used as tablecloth or self coverings with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope that was used to frame the picture. Picasso combined painting with already existing materials. As mentioned in the name of the work, Picasso give clues of the parts of it. For instance the oval canvas and the rope around it represent the table. Pasted chair caning signifies the chair within the table. On the table folded paper shadow represent newspaper. Further there is a cut out lemon painted onto the table. The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness. This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas.

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
  \caption{Dick Jewell, Found Photos, 1978}
  \label{fig:DickJewell_FoundPhotos}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
  \caption{Filomena Cruz, Road Kill, 2014, Photography}
  \label{fig:FilomenaCruz_RoadKill_ReVista}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

@@

They build their musical instruments from what is available around. This project can be seen as a bricolage practice. Dictionary meaning; something constructed using whatever was available at the time. \quotes{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \citep{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \citep{levi1966savage}.

\quotes{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}

@@

In the scope of painting different than the works in the previous chapter (paintings on tea bags and coffee cups) historical potraits of notable people are painted onto the flattened aluminum drink cans which are disposable objects. The people in the figure X is General Jefferson C. Davis who was an officer at United States Army in 19th-century. Selected persons can be viewed as a member of the higher or ruling class of society. Therefore Kim Alsbrooks, painter of these works, might have thought that to make trash is more valuable, their face will be good. Or vice versa. She probably use trash to criticize social elite of that time.

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
  \label{fig:Alsbrooks}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, Art Bin}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

@@

Examples are not limited with these. Even if \quotes{trash is dirty and smelly trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

### 2015-12-29 chapter4_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7

%
%
% TODO: Burada geçmiş, şimdiki zamanlara dikkat etmek gerek.
\section{The Statement}
% TODO Ekolojik, harmful, iğreç falan diye de değinmek gerekli bence.
% --disgusting, abject, unattractive, harmful to the people and nature--
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless and disgusting. Contrary to the common approach as Michael Thompson, author of the book Rubbish Theory, stated "one man's trash is another man's treasure".

@@

% [SODA CAPS]
I remember from my childhood that we were collecting soda caps and played with them. We were looking everywhere to collect them. Some caps were found less and they worth more in the game. We put them on the railways to make them flat. After the train had passed we had perfect flat caps for our games. At that time, it was not waste for us. It has a value and part of our games and indispensable source of fun. The notion of playing with it can be related with the Picasso's collage -"Still Life with Chair Caning"-- mentioned previously. He pasted letters of the French word "JOU" means "game" signifying that playing with the materials. We were already playing with trash while we were child. Therefore, it can be better understand that while Picasso said that "every child is an artist".

% [VASVIYE HOCA]
Another important memory is from my primary school teacher. When I was at third class, our teacher wanted us to bring colorful papers to make something (whatever it is I do not remember now). The day after we brought some colorful paper that was bought from stationery store. Our papers' shape and color looked same. However her papers were different in every dimension. They were cut out from packages and advertisements. I remember clearly that she suggested that same for us. "Do not throw out packages, look for the useful parts and keep them to use later." Whenever I am going to throw something away, this comes to my mind. Can it be reused? Every time it is not obvious that how can it be useful, but at some point it becomes an indispensable practice. Further, this practice is also support to the bricolage methodology. Keeping many things makes easier to build (or produce) whatever at hand.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:landfill_harmonic-sax}
    \end{subfigure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:landfill_harmonic-violin}
    \end{subfigure}
    \caption{Examples of previous works}
    \label{fig:animals}
\end{figure}

[image of previous works.]

@@

% NEW PART [collecting] 
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that "Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question 'Why was this discarded?'". [SUSAN STRASSER p6] I applied these instructions to my case and I checked some points regularly and seeked the reason of why was it discarded. Details will be given later for each objects.

@@

%[owner of disard]
"The question of who owns these discards is not trivial" \cite{zimring2012encyclopedia}. The answer of it is not trivial and sometimes it makes me uncomfortable because of feeling that stealing that someone elses objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.

% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
Trash is also regarded differently, depending on where you live. Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said. But when the same student went to Beverly Hills to go through trash, the police were nearly called. “Who decides what is public and what is private? How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?” Zubiaurre said.

@@

%[people]
% Bu kısmın daha güzel anlatılması gerekli.
% TODO ref.
As mentioned previously many people contributed to the project by collecting. Whenever i meet my friends I ask them to save their discard. The importance of collaboration with them can be understood the term "citizen science" which is “defined as scientific research performed in part or in whole by volunteers who are not professional scientists” [REF]. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

@@

[disposable paper, packaging]
Collected items are mainly disposables ones. Most of them are paper or contains paper pulp. The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China. It is fundamental medium for writing, reading, education, communication, information storage and many others. Its role in the development of human civilization can not be neglected. (Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people. On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage. Further it is easy to find and collect them. Even if it is thrown out, still appropriate for painting and writing.

@@

Since paper is both biodegradable and a renewable resource, it is selected by some of corporation for their products to show their respect to the nature. The motivation why they use can be seen their notes printed on the papers.

[images here.]

% meaning of paper for me.
% TODO buraya bir şey eklenecek.
Seeing papers on the waste bin is a disappointment for me. As stated by the artist "failure of imagination".

@@

[kağıt yığını fotoğrafı]

\textbf{Burger King packages} are collected from the office where I work. At launch time, some of the colleagues order the meal from Burger King which is a global chain of hamburger fast food restaurants. Meals are delivered to the office with paper packages. The package of the meal is collected and used as a cover of notebooks. Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy. Some people think that it is disgusting because of greasy onto it. But immediately I replied them just not you eat that greasy fires so what is wrong with it. At that time what Susan Strassed said comes my mind. (it fits here)

@@

\textbf{Tea bags] are collected from my friend. Their a couple of consumption of tea and their covers.

\textbf{Banka sıra fişleri} my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
% [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili. Bu toplama işlemi normal hayatın içine sızıyor(infiltrate the life). iş bankası örneğinde anlatılabilir. bir de art gallery found object örneği verilebilir.
\textbf{Elginden gelen kağıtlar}
\textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.
\textbf{Others} collected items are not limited with these by the remanings are little to open a new category.

as it can be seen here there are various types of paper and most of them some memories for me.???

@@

[IMAGE experiments with trees.]

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
        %\caption{Sax}
        \label{fig:exhibition1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
        %\caption{Violin}
        \label{fig:exhibition2}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
        %\caption{Violin}
        \label{fig:exhibition3}
    \end{subfigure}
    \caption{Installation try outs}
    \label{fig:exhibition}
\end{figure}

@@

% TODO defterle ilgili şeyleri buraya taşı. hepsi belli seriler ve isimler altında toplandı. bu seriler onların nasıl oluştuklarına dair ip uçları veriyor.

@@

\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner. As mentioned previously the objects are bring their history. They are not blank. Heterogen, hiybrid. It can be one of the examples of this argument.

@@

%
%
\subsection{Exhibition}
Especially it is the most hard topic in the development of the thesis. To find a place for the notebooks is great issue for me?

@@

@@

\textbf{Alternative art space.}

bu işin alternatif bir yer olduğunu düşünürken de aslında nasıl bir alternatif olduğuna torun örnek olabilir.

From another point exhibiting it from a art fallery which is different.

Torun describe itself as a place for free place for sharing art. Open to everybody. Makes open call to the others. Middle of the house.

People can take with them.

Özgür ortam, kamera yok, evlerin arasında.

[IMAGES of torun]

%
%
\subsection{Website}
As I think that finding a place the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.

Mainly websites displays the (hi)story of notebooks. Further it is a place to track the journey the notebooks. As I claimed that it is not a finished work. It does not completed transformation. It always continues. Therefore a website that anyone can reach share their progress via website. Anyone can later discover how they turned to new things etc.

Collect peoples comment with this notebooks. As I leave notebooks different places I do not have connection with people who take them. This website also will help to collect/share peoples ideas about the notebooks.

It will contains a section for how notebooks are produced and the story behind it. The purpose is to record the creative process and share with the others. Revealing the process is significant to demystifiying the truth about the project. It makes it more clear that the object used here is actually transformed from something else.

\textbf{Why website?} Maybe you can think that there are different methods to accomplish recording and sharing the process. In a gallery on a single table or a room it can be succeed. However it like the idea that website can evolve by time as this work evolve in time. I think it matches perfectly. This is not a finished work, it continues and so the website also.

It is also co-authored work. Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them. After production of papers I also want them to continue as co-authored process. In other words many people will be part of this project. As people see different things on objects and bring them to me. the variety of things is increased in time. Because people sad me that \quotes{I thought that you can use it. Do you collect also these?}. After that time I want to continue as so.

SketchBook Project is also inspired me a lot especially in terms of website. This project provides a platform to people in order to share their works with other people. It contains lots of works from all over the world. Full of creativity and showcase of richness of people's expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

@@

to record and make it available available to the public.

It is placed different locations and the pass the proggress of project is limited in time and place. In particularly through the small boxes placed to the libarary. Therefore website can provide a solution for this.

Ben insanlarin ayagina gitmeyi dusundum. This project is placed where people frequently visit.

The aim of this project is to work on website. Website is a supportive element of it. Therefore I only briefly mention the technical details of website. Common and trusted open source technologies are selected.

Served from github pages. Images are are sefved from dropbox.

Website can be accessible through the this address http:\\kulü.be\notebook-project. Domain name kulü.be belongs to me and roject placed under a directory of it.

Technical information. Website is coded by me with the open source libraries and frameworks. Its code also available at this address. Site is hosted by github which is code repository. Pages are generated by jekyll which is a static website generatir through it som repetive works are can be easily automobized and modilarized.

Content of website.

Functionalities of website.

Future works.

Users or visitors can see the notebook series is made. Each notebook serie has a detailed explanation. It can be viewed at there.

It can accessible through the internet. Richer media. Covergence of analog and digital media.

@@

From one point of view it can bee seen that website function visitors book.

Components of website:
- Images of notebooks. 
- Descriptions of notebooks.
- Collected materials.
- Comment and sharing.
- subscribing to email.
- hastag ile filtreleme.

- event photos.
- event announcement.
- videos.
- essays, writings, related word. content related with this topic.

framework to analyze the work.

This thesis and presentation will also be added to the website.

adding different dimension to the project.

% seri numbers and the name of notebook are written inside of the notebooks. How this numbers are given.

Into the notebooks a sticker which contaons qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.

[qr image]

If someone share their work through social networks it betracked and can be viewed in the website. Social networks. Entegration with them.

People can be abke to add their comment to the website. How they are using their notebooks will be showed through it.

People can be able to subscribe to the newsletter to get updates about the project.

Tum bu yapilanlarin uzerine gene de yapilabilecekler var. Kisaca bunlardan bahsetmek istiyorum.

Websitesi ozellikle proje ileride devam edebilsin diye tasarlandi.

In the future all the discussions and research can be moved to the website that people get reach more information about the subject.

Website will function as a platform to get into touch with people. People leave their comments.

The project will be continued after thesis project. New features can be added to the website. New events can be held. All the progress up to now forms the core of the project. In the future it is planned that through the website people can be able to request to get notebooks. Thus project becomes more accessible to the othse people. Moreover notebooks done by others from trash can be added to the website. Beyond notebooks various objects transformed from trash can find a place.

@@

% MAYBE LATER
% [Standartlar, Dönüştürme seviyesi] endüstriyel standartlar, kaplar ve kağıtlar hep bir şekilde bir birleriyle boyut olarak uyuşuyorlar. İlk başlarda kesip biçmeye daha çok ihitiyaç duyarken zamanla basit katlamalar işimi görmeye başladı. Ne kadar az müdahele bulunursam aslında o kadar çok geldiği yerin özelliklerini o kadar çok temsil ediyordu. Bu da benim hoşuma gidiyordu. Kolaj mantığı işte abi. Ne kadar çok değiştirmek dönüştürmek istiyorsun. Burda şöyle bir durum var. çöpleri hiç tanınmayacak bir hale de getirebilirsin. Bu şekilde kimse onların farkına bile varmaz. Ya da neredeyse olduğu gibi kullanırsın. Yani uygulanan dönüştürmenin derecesi çok önemli burada..

>>>>

%
%
% TODO: Burada geçmiş, şimdiki zamanlara dikkat etmek gerek.
\section{The Statement}
% TODO Ekolojik, harmful, iğreç falan diye de değinmek gerekli bence.
% --disgusting, abject, unattractive, harmful to the people and nature--
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless and disgusting. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.

@@

% [SODA CAPS]
I remember from my childhood that we were collecting soda caps and played with them. We were looking everywhere to collect them. Some caps were found less and they worth more in the game. We put them on the railways to make them flat. After the train had passed we had perfect flat caps for our games. At that time, it was not waste for us. It has a value and part of our games and indispensable source of fun. The notion of playing with it can be related with the Picasso's collage work \quotes{Still Life with Chair Caning} mentioned previously. He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials. We were already playing with trash while we were child. Therefore, it can be better understand that while Picasso said that \quotes{every child is an artist}.

% [VASVIYE HOCA]
Another important memory is from my primary school teacher. When I was at third class, our teacher wanted us to bring colorful papers to make something (whatever it is I do not remember now). The day after we brought some colorful paper that was bought from stationery store. Our papers' shape and color looked same. However her papers were different in every dimension. They were cut out from packages and advertisements. I remember clearly that she suggested that same for us. \quotes{Do not throw out packages, look for the useful parts and keep them to use later.} Whenever I am going to throw something away, this comes to my mind. Can it be reused? Every time it is not obvious that how can it be useful, but at some point it becomes an indispensable practice. Further, this practice is also support to the bricolage methodology. Keeping many things makes easier to build (or produce) whatever at hand.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.30\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
    \end{subfigure}
    \caption{Examples of early works}
    \label{fig:EarlyWorks}
\end{figure}

@@

% NEW PART [collecting] 
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that 
\begin{singlespace}
\begin{quote}
Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
\end{quote}
\end{singlespace}
I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.

@@

%[owner of disard]
\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}. This question makes me uncomfortable because of feeling that stealing that someone elses' objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.

% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
%Trash is also regarded differently, depending on where you live. Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said. But when the same student went to Beverly Hills to go through trash, the police were nearly called. “Who decides what is public and what is private? How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?” Zubiaurre said.

@@

%[people]
% Bu kısmın daha güzel anlatılması gerekli.
% TODO ref.
As mentioned previously many people contributed to the project by collecting. Whenever i meet my friends I ask them to save their discard. The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

It can be viewed as a co-authored work. Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them. After production of papers I also want them to continue as co-authored process. In other words many people will be part of this project. As people see different things on objects and bring them to me. the variety of things is increased in time. Because people sad me that \quotes{I thought that you can use it. Do you collect also these?}. After that time I want to continue as so.

@@

%[disposable paper, packaging]
Collected items are mainly disposables ones. Most of them are paper or contains paper pulp. The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China. It is fundamental medium for writing, reading, education, communication, information storage and many others. Its role in the development of human civilization can not be neglected. (Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people. On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage. Further it is easy to find and collect them. Even if it is thrown out, still appropriate for painting and writing.

@@

Since paper is both biodegradable and a renewable resource, it is preferred by some of corporations for their products to show their respect to the nature. The motivation why they use can be seen their notes printed on the papers (Figure \ref{fig:NoteOnPackage}).

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
  \caption{Recycling notice on the package}
  \label{fig:NoteOnPackage}
\end{figure}

% meaning of paper for me.
% TODO buraya bir şey eklenecek.
%Seeing papers on the waste bin is a disappointment for me. As stated by the artist Aaron Kramer \quotes{Trash is the failure of imagination} \cite{meyer2007turning}.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
  \caption{Collected materials}
  \label{fig:CollectedAllTogether}
\end{figure}

\textbf{Burger King packages} are collected from the office where I work. At launch time, some of the colleagues order the meal from Burger King which is a global chain of hamburger fast food restaurants. Meals are delivered to the office with paper packages. The package of the meal is collected and used as a cover of notebooks.

%Also one paper package is used for French fries which is greasy and paper is very good to absorb greasy. Some people think that it is disgusting because of greasy onto it. But immediately I replied them just not you eat that greasy fires so what is wrong with it. At that time what Susan Strassed said comes my mind. (it fits here)

@@

\textbf{Tea bags} are collected from my friend. Their a couple of consumption of tea and their covers.

\textbf{Order slips} are collected from bank office my discovery at bank. opening all perceptions. After that I really convinced that I am really looking for trash everywhere every time.
% [Everywhere, everytime, Life practice.] En başta bahsettiğim everywhere, everytime aslında collecting ile çok yakından ilgili. Bu toplama işlemi normal hayatın içine sızıyor(infiltrate the life). iş bankası örneğinde anlatılabilir. bir de art gallery found object örneği verilebilir.

\textbf{Elginden gelen kağıtlar}

\textbf{Bilkent kağıtları} % bu kısım found photos ile ilişkilendirilebilir.

\textbf{Others} collected items are not limited with these by the remanings are little to open a new category.

%as it can be seen here there are various types of paper and most of them some memories for me.???

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
    \end{subfigure}
    \caption{Experiments with collected paper}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
        %\caption{Sax}
        \label{fig:exhibition1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
        %\caption{Violin}
        \label{fig:exhibition2}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
        %\caption{Violin}
        \label{fig:exhibition3}
    \end{subfigure}
    \caption{Installation experiments with models}
    \label{fig:exhibition}
\end{figure}

@@

@@

\textbf{Puzzle.} Papers inside of the notebooks are cut out from very big and long banner (Figure \ref{fig:Banner_1}). As mentioned previously the objects are bring their history. They are not blank. Heterogen, hiybrid. It can be one of the examples of this argument.

@@

%
%
\subsection{Exhibition}
Especially it is the most hard topic in the development of the thesis. To find an appropriate place for the notebooks is great challenge for me.

@@

Notebooks are places where people frequently visit such as computer desks.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
    \end{subfigure}
    \caption{Example placement at Bilkent}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

Through this project another exhibition alternative is thought. In the notable museums and art galleries there are gift shops that people can buy souvenirs. Often they are mass produced imitations and replicas of well-known artists work embedded various objects such as cover on the notebooks. At this point I image an art space you can buy these types of items freely. In other words alternative to the existing approach this types of gadgets. Another alternative interpretation can be giving away different that the industrial items such as notebooks from trash as in my project. For this type of approach Torun is a great place to show my notebooks and give them away. Torun describe itself as a place for free place for sharing art. Open to everybody. Makes open call to the any artist. There are no security cameras on this gallery therefore no one is watching you at there. This idea shared with Torun and they accepted it. However Torun will opened after 14th of the January currently I just took some photos at there.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
    \end{subfigure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
    \end{subfigure}
    \caption{Example placement at Torun}
    \label{fig:ExperimentWithPaper}
\end{figure}

%
%
\subsection{Website}
As I think that finding a place to the discarded items is one of the main purposes of this project. As it finds a place in people's life again, it also finds another place in the digital space.

Mainly websites displays the (hi)story of notebooks. Further it is a place to track the journey the notebooks. As I claimed that it is not a finished work. Transformation of it does not completed. It always continues. Therefore a website that anyone can reach and share their progress via website  Anyone can later discover how they turned to new things.

As I leave notebooks different places I do not have connection with people who take them. This website also will help to collect/share peoples ideas about the notebooks.

It will contain a section for how notebooks are produced and the story behind it. The purpose is to record the creative process and share with the others. Revealing the process is significant to demystifiying the truth about the project. It makes it more clear that the object used here is actually transformed from something else.

Maybe it can be thought that there are different methods to accomplish recording and sharing the process. In a gallery on a single table or a room it can be succeed. However it like the idea that website can evolve by time as this work evolve in time. I think it matches perfectly. This is not a finished work, it continues and so the website also.

%SketchBook Project is also inspired me a lot especially in terms of website. This project provides a platform to people in order to share their works with other people. It contains lots of works from all over the world. Full of creativity and showcase of richness of people's expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

@@

Website can be accessible through the this address http:\\kulu.be\\notebook-project. Domain name kulu.be belongs to me and project placed under a directory of it. Website is coded by me with the common and trusted open source libraries and frameworks. Its code also available at this address. Site is served from GitHub pages which provides free website hosting. Pages are generated by Jekyll which is a static website generator through it some repetitive works are can be easily automatized.

@@

Into the notebooks a sticker which contains qr code and short description with the address of website is pasted. People can able to reach more information through this reminders.

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
  \caption{QR Code sample}
  \label{fig:Banner_1}
\end{figure}

Through the website people can be able to subscribe to the newsletter to get updates about the project. People can be able to add their comment to the website. How they are using their notebooks will be showed through it. Website will function as a platform to get into touch with people. From one point of view website can bee seen as a visitors book.

In the future all the discussions and research can be moved to the website that people can reach more information about the subject. This thesis and presentation will also be added to the website.

All the progress up to now forms the core of the project. However it is not limited with it. The project will be continued after this thesis completed. New features will be added to the website. In the future it is planned that through the website people can be able to request to get notebooks. Thus project becomes more accessible to the other people. Moreover notebooks done by others from trash can be added to the website. Beyond notebooks various objects transformed from trash can find a place in the website.

@@

% MAYBE LATER
% [Standartlar, Dönüştürme seviyesi] endüstriyel standartlar, kaplar ve kağıtlar hep bir şekilde bir birleriyle boyut olarak uyuşuyorlar. İlk başlarda kesip biçmeye daha çok ihitiyaç duyarken zamanla basit katlamalar işimi görmeye başladı. Ne kadar az müdahele bulunursam aslında o kadar çok geldiği yerin özelliklerini o kadar çok temsil ediyordu. Bu da benim hoşuma gidiyordu. Kolaj mantığı işte abi. Ne kadar çok değiştirmek dönüştürmek istiyorsun. Burda şöyle bir durum var. çöpleri hiç tanınmayacak bir hale de getirebilirsin. Bu şekilde kimse onların farkına bile varmaz. Ya da neredeyse olduğu gibi kullanırsın. Yani uygulanan dönüştürmenin derecesi çok önemli burada...
